
\recipe{Eggs in a Basket}

\recipecolumn{
	\begin{itemize}
		\item Slice of Bread
		\item Egg
		\item Butter
		\item Black Pepper
		\item Green Onion (optional)
	\end{itemize}
}{
	\begin{enumerate}
		\item Heat pan to medium-low, coat with small amount of butter
		\item Use cup to make hole in bread (place bread cutout aside)
		\item Crack egg into hole, and cook 1 minute until egg creates seal with bread
		\item Flip bread slice, allowing other side of the hole to be sealed with egg. Cook desired amount
		\item After cooking garnish with salt and pepper and thinly sliced green onions.
	\end{enumerate}
}

\recipe{Easy French Toast}

\recipecolumn{
	\begin{itemize}
	\item 2 eggs (beaten)
	\item $\frac{1}{4}$ cup coffee creamer (any flavor)
	\item 1 Tbsp Cinnamon
	\item 3 Slices Bread (Any kind)
	\item Butter
	\end{itemize}
}{
	\begin{enumerate}
	\item Pour coffee creamer into beaten eggs and top with cinnamon, then beat further. 
	\item Bathe bread in egg mixture and melt slice of butter in pan on medium heat. Place bread in pan and flip after 1-2 minutes. 
	\item Top with nutella or syrup. 
	\end{enumerate}
}


\recipe{Stovetop Granola}

\recipecolumn{
	\begin{itemize}
		\item Butter;
		\item Olive Oil;
		\item Brown Sugar;
		\item Nutmeg;
		\item Oats;
		\item Almonds (chopped);
		\item Dried Cranberries;
		\item Desicated Coconut (optional);
	\end{itemize}
}{
	\begin{enumerate}
		\item Heat up oil and toss oats in the pan on medium heat
		\item Cook oats until they start to brown and crisp. Place oats aside in a bowl and melt butter in same pan
		\item Place brown sugar and nutmeg in pan as well and toss in oats
		\item Let oats get coated in brown sugar mixture, then add other ingredients
		\item After cooking, let cool and store in a container for later
	\end{enumerate}
}



\newpage
\recipe{Banana Pancakes}

\recipecolumn{
	\begin{itemize}
		\item 1 Banana (diced)
		\item Brown Sugar
		\item Canola Oil
		\item Pancake Batter
		\item Salt
	\end{itemize}
}{
	\begin{enumerate}
	\item Heat the oil on medium heat. Place diced banana in pan
	\item Add brown sugar to pan and stir till pudding-like 
	\item Add salt to mixture at end
	\item Stir banana mixture into pancake batter
	\item Make pancakes as normal.
	\end{enumerate}	
}


\recipe{Cornbread Scramble}

\recipecolumn{
	\begin{itemize}
		\item Cornbread (Large Chunks);
		\item Butter;
		\item Salsa;
		\item Eggs;
		\item Milk;
		\item Sausage (or Chorizo);
		\item Cheese;
	\end{itemize}
}{
	\begin{enumerate}
		\item In a bowl, whisk eggs milk and salsa together
		\item Place butter in a pan and allow to melt under medium heat
		\item Cook sausage thoroughly in pan and place into egg mixture
		\item Place cornbread pieces on pan, and after 2 minutes, cover in egg mixture
		\item Periodically scramble eggs in pan so as to mix cornbread and eggs
		\item Turn to low heat and top with cheese and hot sauce (optional) and cover pan for 3 minutes
		\item Serve with Tortillas
	\end{enumerate}
} 
