

The following book is my tome to a successful college lifestyle. It is by no means perfect for everyone. The recipes and systematic approach in this book are meant to embody one word: simplicity. In the college world, there is such a whirlwind of things to do that sometimes retaining a shred of simplicity is the best therapy. Learning to cook is a skill that serves a dual purpose: utility, and entertainment. 

For utility, it is obvious, we need to eat. We need to sustain our bodies with the correct nutrients in order to function. Every university student knows how dreadful it is to get sick. Not because you are not feeling well (although that is definitely true) but because of the classwork that you miss. You miss the natural cycle of productvity that you have built up over the past couple of weeks. A healthy diet is a irreplaceable way to make sure that you maintain this hard-earned cycle. 

The term ``healthy'' has an incredibly misunderstood connotation when coupled with the work ``diet''. These words paint a picture of calorie counting, and restricting yourself to only what you have to eat. Does that sound like fun? Does it sound tasty? No way. Well-balanced means that you should be able to have choices, and why shouldn't these choices be tasty? 

% Revise this paragraph
Entertainment has its own value to an individual. Do you want to impress a guest? Do you want to impress a date? It suffices to say that cooking good food is a sure way to impress someone. To develop a technique and a flair for cooking is entertaining in its own right. If you are not looking to impress other people, at least with good cooking you can entertain your tastebuds! It sounds like a trivial thing, but after one of these meals, you will never want ramen again. 

% Section on making time.
Cooking has one tiny cost though. The most important commodity that anyone has is time. This is especially so for college students. Cooking takes time, and while it is worth it, it seems hard to make the time for it in a busy schedule. Another major aim of this book is to suggest prior planning that can make cooking much more efficient.\\
So make the time, entertain yourself, and enlighten your taste buds.
\\\\
\textit{- Arjun} 

